Quantifying the rock-paper-scissors effect

### 2021-02-06 inst/rock_paper_scissors_monster.Rmd
consistentify chess

```{r,chesstable}
o <- matrix(c(22,NA,8,13,23,NA,NA,12,10),3,3)
dimnames(o) <- list(
    match=c("T_vs_A","A_vs_K","T_vs_K"),
    player=c("Topalov","Anand","Karpov"))
o
```

@@

```{r,showchess}
chess
maxp(chess)
```

@@

```{r,binomtest}
binom.test(sum(diag(o)),sum(o,na.rm=TRUE),alternative="greater")
```

@@

>>>>

```{r,chesstable}
chess_table <- as.matrix(read.table("chess.txt"))
dimnames(chess_table) <- list(
    match=c("T_vs_A","A_vs_K","T_vs_K"),
    player=c("Topalov","Anand","Karpov"))
chess_table
```

@@

```{r,showchess}
chess <- saffy(chess_table)
chess
chess_maxp <- maxp(chess)
chess_maxp
```

@@

```{r,binomtest}
binom.test(sum(diag(chess_table)),sum(chess_table,na.rm=TRUE),alternative="greater")
```

@@

### Package dataset

Following lines create `chess.rda`, residing in the `data/` directory of the package.

```{r,label=savechessdataset}
save(chess_table,chess,chess_maxp,file="chess.rda")
```
